\documentclass[%singlesided,
               singlesided,
               paper=a4,
               fontsize=10pt
              ]{my-resume}

\usepackage[none]{hyphenat}%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% set geometry
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setlength\highlightwidth{8cm}
\setlength\headerheight{7cm}            % note that margintop gets added to this value, i.e. the header bar is 5cm
\setlength\marginleft{1cm}
\setlength\marginright{\marginleft}      % needs to be 1.5 times to be actually equal. why?
\setlength\margintop{1cm}
\setlength\marginbottom{1cm}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FONTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\RequirePackage{fontspec}
\setmainfont{Arial}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COLORS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\colorlet{highlightbarcolor}{white}
\colorlet{headerbarcolor}{blue}

\colorlet{headerfontcolor}{white}
\colorlet{positionfontcolor}{bronze}
\colorlet{summaryfontcolor}{silver}
\colorlet{accent}{blue}
\colorlet{heading}{blue}
\colorlet{emphasis}{red} %red
\colorlet{body}{blue}
\colorlet{skillsectioncolor}{teal}
\colorlet{jobtitle}{teal}
\colorlet{jobdatefontcolor}{gray}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% set document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\name{Sruthi Devi M P }
\position{\textbf{Senior Software Engineer} \hfill \normalsize \textit{Australian Permanent Resident}}
\tagline{Software Engineer with 8+ years of professional experience in enterprise-scale application development at a Fortune 500 Company. Expertise in database design, Microsoft .NET application development and B2B integrations. Hands-on experience in complete Software Development Life Cycle (SDLC) involving design, development, unit testing, security review, and post-production support of 15+ large-scale mission-critical applications. I thrive on innovation and am eager to contribute my skills and knowledge to a team building future-ready digital solutions. % to build future-ready digital solutions, and transform business.
}
%\photo[round]{picture.jpg}{\dimexpr \headerheight-\marginbottom}   % make photo exactly match the header with margintop/marginright/marginbottom as margin

\makeheader

\highlightbar{

    \section{Contact}
    
    \email{devisruthi@gmail.com}
    \phone{0416 352 241}
    \location{Melbourne, Victoria}
    \vspace{0.5em}
    %\homepage{nicokrieger.com}{https://www.nicokrieger.de}
    \github{github.com/devisruthi}{https://github.com/devisruthi}
    \linkedin{linkedin.com/in/sruthi-devi/}{https://www.linkedin.com/in/sruthi-devi/}
    
    \section{Skills}
    
    \skillsection{Application Development}
    \skill{Microsoft .NET}{5}
    \skill{Transact SQL}{5}
    \skill{C\#}{5}
    \skill{Webforms}{5}
    \skill{.NET Core, EF Core}{4}
    \skill{Microsoft Azure Storage}{4}
    \skill{Entity Framework}{4}
    \skill{HTML,CSS,Javascript}{4}
    \skill{LINQ}{4}
    \skill{MIS Reports, SSRS}{4}
    \skill{.NET MVC, WPF}{3}
    \skill{Modern Frontend \\ \footnotesize{( React, Redux,\\
    Bootstrap, Material UI )}}{4}
    \skill{Azure}{4}
    
    \vspace{1em}
    \skillsection{Software Integration}
    \skill{Web Services}{5}
    \skill{RESTful API}{5}
    \skill{API Security \\{\footnotesize (OAuth 2.0, API Keys,\\Basic Authentication)}}{5}
    \skill{Data formatting \\{\footnotesize (JSON, CSV, XML)}}{5}
    \skill{Open API, Swagger}{4}
    %\skill{RPC, WCF}{2}
    %\skill{SAP Gateways, WCF}{2}
    

}
\mainbar{
    \section[\faMortarBoard]{Education}
	\job{Sep 2021 - Sep 2022}
	{University of Birmingham}
	{Masters in Artificial Intelligence and Computer Science}
	{
		\educationrole{Recipient of Chancellors Academic Merit Award.}
		\educationrole{Secured High Distinction (84\%) with GPA 4.0 (scale of 4.0).}
		%\educationrole{MSc project nominated for demo in University Project Expo.}
 	}
	
	\job{Jun 2008 - Mar 2012}
	{University of Calicut}
	{Bachelor of Technology in Computer Science}
	{
		\educationrole{Placed in First Class with Honours (Aggregate 78\%).}
		\educationrole{Recipient of Central Sector Scholarship consistently all the 4 years for academic excellence.}
	}

    \section[\faGears]{Professional Experience}
    \job{May 2023 - Present}
    {Digital Biz Solutions - DBiz.ai (Melbourne, Australia)}
    {Software Engineer}
    {
    	\jobrole{ Development and maintenance of web portal to manage multi cloud services and associated networks for a telecom client.}
    	\jobrole{ Development and implementation of scalable, secure and reliable cloud architectures on Microsoft Azure Platform.}
    	\jobrole{ Conduct spike, POC and upgrade application components to latest .NET versions as well as refactor  to microservices.}
    }

    \job{Oct 2015 - Oct 2020}
    {Bharat Petroleum Corporation Limited (Mumbai, India)}
    {Senior Software Engineer \normalsize(Assistant Manager)}
    {
    	\jobrole{ Designed and developed enterprise-scale applications serving more than 80 million consumers in .NET platform.}
    	\jobrole{ Refactored \& optimized high-transactional modules (1 million transactions / second) of a monolithic application to services.}
    	\jobrole{Researched \& presented cloud-based solutions for business challenges (document management, analytics \& ai services). }
    	\jobrole{Integrated in-house payment system with Amazon, Paytm, etc. achieving 80 percent customer conversion.}
    	%\jobrole{Mentored team of 4 junior developers in migration of customer portal from Java to .NET platform.}
    	%\jobrole{Co-ordinate with teams to assess third-party software products and present insights to higher management for vendor selection.}
    	%\jobrole{Provided feedback to junior engineers for proposed solutions and coaching on domain knowledge and best practices. }
    	%\jobrole{Conducted code reviews and cordinated security reviews to ensure high-quality secure application development.}
    	%\jobrole{Liaised with internal teams for SQL 2016 \& TFS 2017 migration, release automation, and .Net 4.6 upgrades.}
        }

}  
\makebody

\clearpage
\pagestyle{empty}
\highlightbar{
	
	\section{Skills}
	
	
	\vspace{0.5em}
	\skillsection{Design and Architecture}
	\skill{Database Design}{5}
	\skill{Monolithic}{5}
	\skill{Service oriented}{5}
	\skill{Microservices}{3}
	\skill{Event Driven Design}{3}
	
	\vspace{0.5em}
	\skillsection{General Skills}
	\skill{Agile Development}{5}
	\skill{JIRA}{4}	
	\skill{Azure Cloud}{4}
	\skill{Version Control \\{\footnotesize (TFS, GIT)}}{5}
	\skill{CI/CD , Azure DevOps}{4}
	%\skill{IIS}{5}
	%\skill{NLog}{4}
	%\skill{OWASP, WAPT}{4}
	\skill{Unit Testing - NUnit, jest }{4}
	\skill{Test Driven (TDD)}{3}
	\skill{Load Testing, JMeter}{3}
	\skill{MongoDB}{3}
	
	
	\vspace{0.5em}
	\skillsection{Artificial Intelligence }
	\skill{Machine Learning}{4}
	\skill{Deep Learning}{4}
	\skill{Azure Applied AI \\Services}{4}
	\skill{Azure ML Studio}{3}
	\skill{Python}{4}
	\skill{MATLAB}{3}
	\skill{Visualization \\{\footnotesize (matplotlib, seaborn)}}{3}
	\skill{Data analytics \\{\footnotesize (numpy, scipy, pandas)}}{3}
	
	\vspace{0.5em}
	\skillsection{Soft Skills}
	\skill{Problem Solving}{5}
	\skill{Analytical Skills}{5}
	%\skill{Quick learner}{5}
	\skill{Inter personal skills}{5}
	\skill{Team Player}{5}
	\skill{Communication}{5}
	\skill{Mentoring}{5}
	
	\section{Certifications}
	\achievement{Machine Learning Specialization}
	\achievement{SAP Certified ERP consultant}
	
	\section{Languages}
	\smallskip % additional skip because tag outlines use up space
	\tag{English}
	\tag{Malayalam}
	\tag{Hindi}
}
\mainbar{
	\jobrole{Mentored team of 4 junior developers in migration of customer portal from Java to .NET platform.}
	
	%\jobrole{Liaised with internal teams for roll out of SQL 2016 \& TFS 2017 migration, release automation, and .Net 4.6 upgrades.}
	
	\jobhighlight{Achievements}
	\jobrole{Consistently rated as top 1\% of employee in 2017-2020.}
	\jobrole{Demonstrated centralized knowledge base system and digital vision projects at Annual Meet.}
	
	\job{Jul 2013 - Oct 2015}
	{Bharat Petroleum Corporation Limited (Mumbai, India)}
	{Software Engineer \normalsize(Executive Officer)}
	{
		\jobrole{Designed and developed B2B \& B2C applications for customer enrollment, sales cycle implementation, stock reconciliation, financial settlement and MIS reports in .NET.}
		\jobrole{Designed database and implemented web services and REST APIs for 15+ B2B integration projects.}
		\jobrole{Automated recurrent data transformation tasks using scheduled SSIS jobs. }
		%\jobrole{Achieved highly availability for Management Information System (MIS) reports with SSRS and scheduled SSIS jobs. }
		\jobrole{Used SQL query optimizations, SSRS, data-driven reports,
		etc. to provision data for audit, BI, and other agencies.}
		\jobrole{Proposed and implemented database partitioning for consumption pattern analysis of 10 million consumers.}
		\jobrole{Implemented phases of Direct Benefit Transfer of LPG Subsidy (DBTL) to consumer's bank in an Agile environment.}
		}
	
		\jobhighlight{Achievements}
		\jobrole{Project DBTL entered Guinness Book of World Records for being the largest cash transfer program.}
		\jobrole{User appreciation at annual event (IS Meet) for consumption pattern analysis implementation under tight deadlines.}
	
	\job{Jul 2012 - Jul 2013}
	{Bharat Petroleum Corporation Limited (Mumbai, India)}
	{Junior Software Engineer \normalsize(Management Trainee)}
	{
		\jobrole{Explored design patterns and refactored 5+ enterprise-scale
			applications using them.}
		\jobrole{Proposed and implemented interactive adobe forms in Asset management application to reduce licensing costs by 30\%.}
	}
	
	\jobhighlight{Achievements}
	\jobrole{Appreciation from Executive Director of BPCL in the product launch meeting.}
	
	\section[\faBriefcase]{Additional Info}
	{   
		\projectinfo{Career Break }{Oct 2020 - May 2023}
		%\projectinfo{Furniture Rental System}{Dec 2020 - Feb 2021}
		%\jobrole{Developed application in MERN (MongoDb, Express, React, Node) stack for renting out furnitures.}
		\jobrole{ Full time parent, Completed Masters, Relocated to Australia.}
		\projectinfo{MSc Project}{Sep 2021 - Sep 2022}
		\jobrole{Developed an AI (Artificial Intelligence) model for COVID-19 detection in chest radiographs with an accuracy of 98\%.}
		\projectinfo{Project - Retail ERP Solution}{Apr 2021 - Dec 2021}
		\jobrole{Developed an ERP solution for retail optical shops developed in Microsoft .NET Core \& Azure, thus ensuring cross-platform support.}
		\jobrole{Designed front-end with Material UI and created Progressive Web App (PWA) to ensure web and mobile support.}
	}
}  
\makebody
\clearpage


\end{document}
